Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-02 sections/srfm.tex
complete section on deterministic approaches

\begin{figure}
  \centering
  \includegraphics{gr/intro/direct-SR-mic}
  \caption{\textbf{Principle of STED microscopy.} \textbf{a:} Shape of
    excitation and ring-shaped depletion beam. \textbf{b:} The two beams are
    superimposed and the sample is scanned. Fluorophores in the center are
    excited and emit spontaneously (yellow dot), while the depletion beam
    induces stimulated emission of the fluorophores in the periphery (black
    dots). \textbf{c:} (left) Line profile of the intensity of the depletion
    beam (red) and probability to induce stimulated emission (black); (center)
    Jablonski diagram of stimulated emission (SE); (right) wavelengths of
    excitation (ex), detection (det) and stimulated emission (SE) superimposed
    on the absorbance/emission spectrum of a fluorescent dye.}
  \label{fig:STED-principle}
\end{figure}

As an example for RESOLFT, the principle of STED microscopy is sketched in
Fig.~\ref{fig:STED-principle}. The excitation spot
(Fig.~\ref{fig:STED-principle}a, top) is superimposed with a second, ring- or
doughnut-shaped spot (Fig.~\ref{fig:STED-principle}a, bottom). The
fluorophores are excited by the excitation light, but only those located in
the center of the minimum of the depletion beam are allowed to emit
spontaneously (yellow dot). The fluorophores at the periphery are de-excited
by the depletion and undergo stimulated emission (black dots).

>>>>

\begin{figure}
  \centering
  \includegraphics{gr/intro/direct-SR-mic}
  \caption{\textbf{Principle of STED microscopy.} \textbf{a:} Shape of
    excitation and ring-shaped depletion beam. \textbf{b:} The two beams are
    superimposed and the sample is scanned. Fluorophores in the center are
    excited and emit spontaneously (yellow dot), while the depletion beam
    induces stimulated emission of the fluorophores in the periphery (black
    dots). \textbf{c:} (left) Jablonski diagram of stimulated emission (SE);
    (center) Line profile of the intensity of the depletion beam (red) and
    probability (prob) to induce stimulated emission (black); (right)
    wavelengths of excitation (ex), detection (det) and stimulated emission
    (SE) superimposed on the absorbance/emission spectrum of a fluorescent
    dye.}
  \label{fig:STED-principle}
\end{figure}

As an example for RESOLFT, the principle of STED microscopy is sketched in
Fig.~\ref{fig:STED-principle}. The excitation spot
(Fig.~\ref{fig:STED-principle}a, top) is superimposed with a second, ring- or
doughnut-shaped spot (Fig.~\ref{fig:STED-principle}a, bottom). The
fluorophores are excited by the excitation light, but only those located in
the center of the minimum of the depletion beam are allowed to emit
spontaneously (yellow dot). The fluorophores at the periphery are de-excited
by the depletion beam and undergo stimulated emission (black dots). The
Jablonski diagram of stimulated emission is shown in
Fig.~\ref{fig:STED-principle}c (left). An incoming photon of the depletion
beam interacts with the excited fluorophore and causes it to de-excite to the
ground state and to emit a photon of the same energy as the incoming
photon. Due to the non-linear relation between intensity and the probability
to induce stimulated emission and the shape of the depletion beam
(Fig.~\ref{fig:STED-principle}c, center), the size of the origin of
spontaneous emission in the center of the depletion beam is decreased. The
wavelength of the depletion beam and thus the wavelength of stimulated
emission is selected such that it lies outside the detection window of the
microscope (Fig.~\ref{fig:STED-principle}c, right), which de-facto switches
fluorophores that undergo stimulated emission to an ``off''-state.

In summary, this directly yields a recording of the fluorophores with a
resolution beyond the diffraction limit (Fig.~\ref{fig:STED-principle}d). The
resolution provided by STED microscopy depends on the intensity $I$ of the
depletion beam and is given by
\begin{equation}
  d_\text{min, STED} = \frac\lambda{2\mathrm{NA}\sqrt{I/I_\text{sat}}}\text,
  \label{eq:resolution-STED}
\end{equation}
which is a modification of Abbe's original equation
(eq.~\eqref{eq:diffraction-limit}). Here, $I_\text{sat}$ is the intensity
required to induce stimulated emission in half of the fluorophores.
